Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-13 paper/paper.tex
appendix edited

We also a Kolmogorov-Smirnov (K-S) test to compare each parameter
distribution in the best $25$ models against the parent distribution
of $2500$ models. 
From a p-value $<0.05$ for a given model parameter, we conclude that
this parameter can be constrained from the observations, as the distribution for
the best $\chi^2$ models is statistically different to the
distribution from the global sample of $2500$ models.

@@

With $14$ free parameters our first concern is discovering which 
parameters matter the most.
From the K-S tests we find that only 3 parameters 
are confidently constrained by \tol's line shape;
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).

This illustrated by the results shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the $1\%$ models with the lowest
$\chi^2/d.o.f.$.  
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
\mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
\jefr{The small uncertainty only says that the increase in
  $\chi^2/dof$ is very steep as you vary a parameter. I don't think you can get larger errors
  with the available data. Simple inspection of Figure 2 shows
  that the errors will be small with the data we have. The
  paremeter uncertainty roughly corresponds to the width of the parabola
  when there is a difference of $\chi^2/dof\sim 1$ from the minimum. In the data we
  have a huge jump of $\chi^2/dof$ of $\sim 5$ between the minimum
  and the nearest data point. }

@@

\jefr{I find this paragraph confusing. Discussing an hypotetical case where
all parameters matter undermines the explanation of our concrete case
where only some parameters matter more. Probably we can remove it}.
{\bf However, larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce
additional radiative transfer effects and thus increase the number of
relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
This means that even  
if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, the rest of parameters
affect the line profile at a level that cannot be neglected.}

As a test we run a small set of $100$ additional radiative
transfer simulations with random values for all parameters, except for
$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $3\sigma$
constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
That is, we have a $30\%$ chance to find good models, which is
significanty higher than the lower $1\%$ success rate if the
parameters were unconstrained.  
\mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
  $P_{cl}$ were run within $3\sigma$. All the other parameters,
  including $v_{\infty}$were
  unconstrained.}

@@

Which model has more
chances to be correct?  
We discard the rotation model by considering that the rotational
velocity of $\sim350$ \kms\ is too high for such a low
mass system.  \mg{I am confused -- are much lower rotational
  velocities not exclude by the priors used?}\jefr{Yes, they are
  discarded, but here we are talking about the most likely value of
  350 km/s.}
\tol's inferred rotational velocity is larger than the
Milky Way's ($\sim200$\kms) while its baryonic mass is one order
of magnitude smaller. 
Furthermore, \tol's structural properties seem to be similar to known dwarf
elliptical galaxies. 
The sample of 7 dwarf ellipticals (dE) observed by
\cite{2003AJ....126.1794G} show similar properties as \tol. 
For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
\tol. 
These dE galaxies have velocity dispersions of $31.1$ \kms and
$44.6$ \kms, respectively,  and their rotational velocities are lower
than $1$ \kms.  
This leads us to prefer the multiphase model as it provides 
a broad consistency with kinematic properties of dE galaxies.

@@

\bibliographystyle{mn2e}
%\bibliography{references}

\begin{thebibliography}{}

@@

@@

Using the total number of degrees of freedom, $d.o.f.=104$ we divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.>35$. \mg{Why was $35$ chosen as a boundary?}\jefr{We
  chose $35$ to match the cut that we used to make the  integrated
  probability distributions. However the nuber itself is
  arbitrary. Ideally we should only chose models with $\chi^/dof$
  higher by $2$ than the lowest $\chi^2/dof$, but we don't have any
  models in that range.}
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.

Figure \ref{fig:tree} shows as an illustration the results for a
single classification tree.
The tree starts with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes, respectively. 
We find that the best classification
yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
The split in two classes is not perfect. 
This means that these 3 parameters are the most useful parameters
in finding models with low $\chi^2/d.o.f.$.
Not having a perfect classification using these three parameter only,
shows that some combinations of the other 11 parameters are also
relevant to find a good fit.

>>>>

We run a Kolmogorov-Smirnov (K-S) test to compare each parameter
distribution in the best $25$ models against the parent distribution
of $2500$ models. 
From a p-value $<0.05$ for a given model parameter, we conclude that
this parameter can be constrained from the observations, as the distribution for
the best $\chi^2$ models is statistically different to the
distribution from the global sample of $2500$ models.  
As a complement (Appendix \ref{appendix}) we also use a random forest
classifier to find the most important parameters in selecting a low
$\chi^2$ mode.

@@

With $14$ free parameters our first concern is discovering which 
parameters matter the most.
From the K-S tests we find that only 3 parameters 
are confidently constrained by \tol's line shape;
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
$10^{-4}$) and $P_{\rm cl}$ (p-value $10^{-4}$).

This illustrated by the results shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the $1\%$ models with the lowest
$\chi^2/d.o.f.$, where we use the total number of degrees of freedom,
$d.o.f.=104$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
\mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
\jefr{The small uncertainty only says that the increase in
  $\chi^2/dof$ is very steep as you vary a parameter. I don't think you can get larger errors
  with the available data. Simple inspection of Figure 2 shows
  that the errors will be small with the data we have. The
  paremeter uncertainty roughly corresponds to the width of the parabola
  when there is a difference of $\chi^2/dof\sim 1$ from the minimum. In the data we
  have a huge jump of $\chi^2/dof$ of $\sim 5$ between the minimum
  and the nearest data point. }

@@

\jefr{I find this paragraph confusing. Discussing an hypotetical case where
all parameters are important undermines the explanation of our concrete case
where only some parameters matter more. Probably we can remove it}.
{\bf However, larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce
additional radiative transfer effects and thus increase the number of
relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
This means that even  
if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, the rest of parameters
affect the line profile at a level that cannot be neglected.}

{\bf As a test we run a small set of $100$ additional radiative
transfer simulations with random values for all parameters, except for
$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $3\sigma$
constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
That is, we have a $30\%$ chance to find good models, which is
significanty higher than the lower $1\%$ success rate if the
parameters were unconstrained.  }
\mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
  $P_{cl}$ were run within $3\sigma$. All the other parameters,
  including $v_{\infty}$, were
  unconstrained. Should we mention this test given that we didn't run
  with a constrain on $v_{\infty}$?}

@@

Which model has more
chances to be correct?  
We discard the rotation model by considering that the prefered rotational
velocity of $V_{m}\sim350$ \kms\ is of the same order as the largest rotational velocity of giant
disc galaxies that have two orders of magnitude more baryonic mass
than \tol\ \citep{2015MNRAS.448.1767C}. 
\mg{I am confused -- are much lower rotational
  velocities not exclude by the priors used?}\jefr{Yes, they are
  discarded, but here we are talking about the most likely value of
  350 km/s.}

Furthermore, \tol's structural properties seem to be similar to known dwarf
elliptical galaxies. 
The sample of 7 dwarf ellipticals (dE) observed by
\cite{2003AJ....126.1794G} show similar properties as \tol. 
For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
\tol. 
These dE galaxies have velocity dispersions of $31.1$ \kms and
$44.6$ \kms, respectively,  and their rotational velocities are lower
than $1$ \kms.  
This leads us to prefer the multiphase model as it provides 
a broad consistency with kinematic properties of dE galaxies.

@@

\bibliographystyle{mn2e}
%\bibliography{references}
\begin{thebibliography}{}

@@

\bibitem[\protect\citeauthoryear{{Courtois}, {Zaritsky}, {Sorce} \&
  {Pomar{\`e}de}}{{Courtois} et~al.}{2015}]{2015MNRAS.448.1767C}
{Courtois} H.~M.,  {Zaritsky} D.,  {Sorce} J.~G.,    {Pomar{\`e}de} D.,  2015,
  \mnras, 448, 1767

@@

We divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.>35$. \mg{Why was $35$ chosen as a boundary?}\jefr{We
  chose $35$ to match the cut that we used to make the  integrated
  probability distributions. However the nuber itself is
  arbitrary to have the $1\%$ of the initial number of models. 
Ideally we should only chose models with $\chi^/dof$
  higher by $2$ than the lowest $\chi^2/dof$, but we don't have any
  models in that range.}
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.

Figure \ref{fig:tree} shows as an illustration the results for a
single classification tree.
The tree starts with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes, respectively. 
We find that the best classification
yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
This means that these 3 parameters are the most useful parameters
in finding models with low $\chi^2/d.o.f.$.
